Hydras \& Co.

### 2023-07-07 doc/chapter-natural-deduction.tex
use latex package turnstile

%%%%%%%%%%%%%% New chapter 
\subsection{Contexts as sets}

@@

Prove the following lemma:
\inputsnippets{FolExamples/MPdiag}

@@

>>>>

%%%%%%%%%%%%%% New chapter 
\section{Contexts as sets}

Let us look again at the proof scripts shown in~\vref{proof:PrfEx2} and \vref{proof:PrfEx3}.
\begin{itemize}
\item The statement of \texttt{PrfEx2} contains a sequence
of hypotheses with two occurrences of \texttt{A}. Moreover, the order in which the 4 hypotheses are listed is determined by the type of the constructor \texttt{MP}  (please look at
Figure~\vref{fig:prf-def}). It would be better to replace this
precise list of hypotheses with ``any list whose elements
belong to the set $\{A, A \arrow B; A \arrow B \arrow C\}$''.

\item In the proof of \texttt{PrfEx3} the \coq user would certainly ask ``How do we apply implication's introduction rule?''.
\end{itemize}

The answer to both questions in~\cite{Goedel}  is the definition of a proof system, derived from \texttt{Prf}, which considers
\emph{sets of hypotheses} (called \emph{systems} in ~\cite{Goedel}) instead of
\emph{list of hypotheses}, thus making abstraction of
repetition and order of appearance of hypotheses in the context.

The new system is simply defined as below:
\inputsnippets{folProof/SysPrfDef}

\subsubsection{Notations}

\begin{itemize}
\item  $\Gamma \sdash A$ for
  (\texttt{SysPrf $L$ $\Gamma$ $A$}).
\item $\Gamma, \Delta$ for $\Gamma\cup\Delta$
\item $\Gamma, A,\dots B$ for $\Gamma\cup\{A \dots B\}$
\end{itemize}

\subsubsection{Examples}

In the following script, we use \texttt{PrfEx2}
as a witness for proving a set-based version of the 
original proof term.

$$A \sststile{\mathrm{S}}{} A$$

\inputsnippets{folExamples/SysPrfEx2}

@@

Prove the following lemma:
\inputsnippets{FolExamples/MPSys}

@@

\subsection{Using properties of sets}

The following three lemmas, from 
\href{../theories/html/hydras.Ackermann.folLogic.html}{Ackermann.folLogic} are direct consequences of \texttt{SysPrf}'s definition.

\inputsnippets{folLogic/Axm}

\inputsnippets{folLogic/SysExtend}

\section{The deduction theorem}

\inputsnippets{Deduction/deductionThm}
